---
title: "Lab assignment 9"
author: "Ruixuan Hu"
date: "11/15/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Assignment - lab 9
1.Submit your solution for the Problem 1 from Activity 9.

1. Consider a function that counts number of odd numbers in a given vector
odd_count =function(x) {
  odd_num = 0
  for(i in 1:length(x)) {
  if(x[i]%%2==1) odd_num  = odd_num+1
  }
  return(odd_num)
}

Write a vectorized form of this function and compare their performance using microbenchmark function from the package microbenchmark.

Run both of the function.

```{r}
odd_count =function(x) {
  odd_num = 0
  for(i in 1:length(x)) {
    if(x[i]%%2==1) odd_num  = odd_num+1
    }
  return(odd_num)
}

```


```{r}
vert_odd_count =function(x) {
  odd_num= sum(x[i]%%2==1)
  return(odd_num)
}

```

Then use microbenchmark.

```{r}
library(microbenchmark)
x<-1e4
microbenchmark(odd_count(x),vert_odd_count(x))
```
Then we can see it is faster.


2.Modify the sorting function (sort_vec) from “Assignment 8” (problem 3) so that it should take an additional argument ascending which causes sorting in increasing order when ‘ascending = TRUE’. In other words, 
sort_vect(c(3, 1, 2), ascending = TRUE) = (1, 2, 3) 
sort_vect(c(3, 1, 2), ascending = FALSE) = (3, 2, 1)


```{r}
sort_vec = function(x,ascending) {

  if (length(x) < 2 ) return (x)

    for (last in length(x):2) { 
      for (first in 1:(last - 1)) {
        if ((x[first] > x[first + 1]) == ascending)  { 
          tmp = x[first + 1]
          x[first + 1 ] = x[first] 
          x[first] = tmp
        
        
          
        } 
      }
    }



 
return(x) 
}

sort_vec(c(3,1,2),ascending = TRUE)
sort_vec(c(3,1,2),ascending = FALSE)
```

3.Consider a simple random walk with starting point 0 and a step -1 or 1. Below is the code with dynamically allocated memory. Write your code with preallocated memory and compare time for both versions using system.time() function (use N = 1000, 10000 and 1000000).


First, Let us start with dynamically allocated memory.
```{r}
N = 1000
data_series = 0 
system.time({for (i in 2:N){
data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
}
})
```

```{r}
N = 10000
data_series = 0 
system.time({for (i in 2:N){
data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
}
})
```
```{r}
N = 100000
data_series = 0 
system.time({for (i in 2:N){
data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
}
})
```

Then let us goes with preallocated memory.
```{r}
N = 1000
data_series = rep(NA,length(x))
system.time({for (i in 2:N){
data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
}
})
```

```{r}
N=10000
data_series = rep(NA,length(x))
system.time({for (i in 2:N){
data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
}
})
```
```{r}
N=100000
data_series = rep(NA,length(x))
system.time({for (i in 2:N){
data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
}
})
```

Also, we can figure out it takes less time.
